---
title: "coursea r-programming assignment2"
author: "kaz yama"
date: "Wednesday, May 20, 2015"
output: html_document
---
The following functions calculate the inverse of the matrix created with the functions. 
However, it first checks to see if the inverse has already been calculated.
If so, it gets the inverse from the cache and skips the computation. 
Otherwise, it calculates the inverse of the matrix 
sets the value of the inverse in the cache via the function in makeCacheMatrix
note makecacheMatrix needs to be initialized after the object is created.
it also uses the properties of inverse & transpose.
```{r}
makeCacheMatrix <- function(x = numeric()) {
  m <- NULL
  set <- function(y) {
    x <<- y
    m <<- solve(y)
  }
  getm <- function() x

  getsolve<- function() m
  list(set = set, getm = getm,
       getsolve = getsolve)
}


cacheSolve <- function(xx,M,...) {
  mm <- xx$getsolve()
  data <- xx$getm()
  if(!is.null(mm)&
         isTRUE(all.equal(data,M))
    ) {
    message("getting cached data1")
    return(mm)
  }else if (!is.null(mm)&
              isTRUE(all.equal(mm,M))
            ){
    message("getting cached data2")
    return(data)    
  }else if (!is.null(mm)&
         isTRUE(all.equal(data,t(M)))
    ){
        message("getting cached data3")
    return(t(mm))
  }
  else if(!is.null(mm)&
              isTRUE(all.equal(mm,t(M)))
    ){
        message("getting cached data4")
    return(t(data))
  }
  else{
  message("solve")
  xx$set(M)
  return(xx$getsolve())
  }
}
```

Testing begin
```{r, echo=TRUE}
B = matrix( 
  c(2, 4, 3, 1, 5, 7,6,8,9), 
  nrow=3, 
  ncol=3) 
BB<-solve(B)
B
BB
B%*%BB
C = matrix( 
  c(4, 9, 2, 3, 5, 7,8,1,6), 
  nrow=3, 
  ncol=3) 
CC<-solve(C)
C
CC
C%*%CC
d=matrix(c(4,14,15,1,9,7,6,12,5,11,10,8,16,2,3,20),nrow=4,ncol=4)
dd=solve(d)
d
dd
d%*%dd

yy2<-makeCacheMatrix(B)
yy2$set(B)

yy2$getsolve()
yy2$getm()

cacheSolve(yy2,B)
cacheSolve(yy2,B)
cacheSolve(yy2,t(B))
cacheSolve(yy2,BB)
cacheSolve(yy2,t(BB))

cacheSolve(yy2,C)
cacheSolve(yy2,C)
cacheSolve(yy2,CC)
cacheSolve(yy2,t(CC))

cacheSolve(yy2,d)
cacheSolve(yy2,d)
cacheSolve(yy2,dd)
cacheSolve(yy2,C)
cacheSolve(yy2,CC)
```

Testing end